\section{Implementation Structure}
\label{sec:structure}

Since Ullman's original search-space pruning algorithm~\cite{1976-ACMJ-Ullman}
published in 1976 there has been an influx of new algorithms attempting to find
tighter subspaces and improved search orders, as well as storing partial results
in graph indexes to allow for faster access.  The most recent, and fastest
algorithms have been in the last 8 years. Notably, these are
QuickSI~\cite{2008-VLDB-QuickSI}, GraphQL~\cite{2008-SIGMOD-GraphQL},
TurboIso~\cite{2013-SIGMOD-TurboISO}, BoostIso~\cite{2015-VLDB-BoostIso}, and
DualIso~\cite{2014-IEEE-DualIso}.

A 2012 comparison of existing algorithms~\cite{2012-VLDB-IsoSurvey} concluded
that QuickSI, and GraphQL were the fastest from among other algorithms including
GADDI, SPath~\cite{2010-VLDB-SPath}, and VF2~\cite{2004-PAMI-VF2}. It created a
common framework for all of the algorithms, that allowed for a more
comprehensive understanding of the way in which these graphs are being
queried. It is essentially broken up into four steps. \textsc{FilterCandidates},
which performs a label search on a given edge.  Once this has been performed
for all vertices, the recursive subroutine \textsc{SubgraphSearch} is
called. Within this routine, there is the function \textsc{NextQueryEdge},
which determines the search order of the query graph, \textsc{IsJoinable}, which
determines whether the proposed match is actually viable, \textsc{UpdateState},
which updates the mapping with the joinable pair, then the recursive call, and
finally, \textsc{RestoreState}, which removes the pair from the mapping. This is
explicitly stated in Algorithm~\ref{alg:gen_query_proc}. Note that a key
difference between this algorithm and the one presented in
\cite{2012-VLDB-IsoSurvey} is that here we have an algorithm that finds an
edge-mapping as opposed to a vertex-mapping, and so the structure is slightly
different. 

\begin{algorithm}
  \label{alg:gen_query_proc}
  \caption{\textsc{GenericQueryProc}$(Q,G)$}
  \SetAlgoLined
  \KwIn{A query graph $Q$, A data graph $G$}
  \KwOut{All subgraph ismorphisms of $Q$ in $G$}

  Initialize the Mapping $M$ to $\emptyset$\;
  \ForEach{$e \in E(Q)$}{
    $\Phi(e)$ \texttt{:=} \textsc{FilterCandidates}$(G,Q,e, \cdots )$\;
    \If{$\Phi(e) = \emptyset$}{ \Return{} \; }
  }

  \textsc{SubgraphSearch}$(Q,G,M,\Phi, \cdots)$\;

  \setcounter{AlgoLine}{0}
  \SetKwProg{subroutine}{Subroutine}{}{}
  \subroutine{\textsc{SubgraphSearch}$(Q,G,M,\Phi, \cdots)$}{
    \eIf{$|M| = |E(Q)|$}{
      \textbf{Report} $M$\;
    }{
      $e$ \texttt{:=} \textsc{NextQueryEdge} $(\cdots)$\;
      $\Phi'(e)$ \texttt{:=} \textsc{RefineCandidates} $(M,u, \Phi(e), \cdots)$\;
      \ForEach{$f \in \Phi'(e)$ that is not yet matched}{
        \If{\textsc{IsJoinable}$(Q,G,e,f, \cdots )$}{
          \textsc{UpdateState}$(M,e,f, \cdots )$\;
          \textsc{SubgraphSearch}$(Q,G,M, \cdots)$\;
          \textsc{RestoreState}$(M,e,f, \cdots )$\;
        }
      }
    }
  }
\end{algorithm}

In the next section we will detail how to go about developing this framework for
existing graphs. Specifically, how we can use temporal information to further
restrict the search space for existing algorithmic paradigms.

\input{postcondition}
\input{preprocessing}
\input{naive_filter_candidates}
\input{naive_refine_candidates}
\input{naive_next_query_edge}
\input{naive_joinable}
